Irt plot extra

### 2022-07-19 manuscript.Rmd
typo fixed in the limtation

- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal reliability coefficients below .70 `r apa((alpha.tab[5,1]),2,F)`. As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”. However, for scales with less than 20 items and at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s $\omega_t$=0.77), while all factors were highly interpretable regarding a common behavioural theme. Thus, we decided to proceed with the five-factor solution.
- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data. However, two additional items covaried in their error variance. By allowing the latter pair (30 $\&$ 41) to covary, the model's error variance attained an improved fit (cf. **Figure 5**). A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items. Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
- The habitual patterns queried in the developed scales might not exhaustively represent all relevant light-exposure-related behaviours. For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status. However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis. Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the behavioural aspects of light exposure in more depth.
- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours. In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall. In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources. The accessibility of the LEBA is also reflected in the “grade level identification” findings suggesting a minimum age of 8.33 years and an educational grade of four or higher. We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.

>>>>

- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal consistencyreliability coefficients below .70 ($\alpha$=`r apa((alpha.tab[5,1]),2,F)`). As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”. However, for scales with less than 20 items and at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s $\omega_t$=0.77), while all factors were highly interpretable regarding a common behavioural theme. Thus, we decided to proceed with the five-factor solution.
- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data. However, two additional items covaried in their error variance. By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit (cf. **Figure 5**). A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items. Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
- The habitual patterns queried in the developed scales might not exhaustively represent all relevant light-exposure-related behaviours. For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status. However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis. Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the behavioural aspects of light exposure in more depth.
- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours. In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall. In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources. The accessibility of the LEBA is also reflected in the “grade level identification” findings suggesting a minimum age of 8.33 years and an educational grade of four or higher. We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.
